### 2019-12-02 Common/chapters/data_processing.tex
Julien and Johan: add screenshots for visualization tool and remake forward propagation screenshot

\textbf{SCREENSHOT}

@@

\textbf{SCREENSHOT}

@@

\textbf{SCREENSHOT}

>>>>

\begin{figure}[!h]
\centering
\includegraphics[width=\textwidth, keepaspectratio=true]{./figures/visualize_lung_dcm.png}
\caption{Visualization of a folder of DICOM files}
\label{fig:visualize_lung_dcm}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=\textwidth, keepaspectratio=true]{./figures/visualize_brain_nii.png}
\caption{Four-dimensional NIfTI visualization}
\label{fig:visualize_brain_nii}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=\textwidth, keepaspectratio=true]{./figures/visualize_liver_raw.png}
\caption{Three-dimensional RAW visualization}
\label{fig:visualize_liver_raw}
\end{figure}
